\begin{thebibliography}{99}

\bibitem{stevens2015aircraft}
Stevens B L, Lewis F L, Johnson E N.
\textit{Aircraft Control and Simulation: Dynamics, Controls Design, and Autonomous Systems}.
3rd ed. Hoboken, NJ: Wiley, 2015.

\bibitem{leishman2006helicopter}
Leishman J G.
\textit{Principles of Helicopter Aerodynamics}.
2nd ed. Cambridge: Cambridge University Press, 2006.

\bibitem{mccormick1995aerodynamics}
McCormick B W.
\textit{Aerodynamics, Aeronautics, and Flight Mechanics}.
2nd ed. New York: Wiley, 1995.

\bibitem{ducard2011fault}
Ducard G J J.
\textit{Fault-tolerant Flight Control and Guidance Systems: Practical Methods for Small Unmanned Aerial Vehicles}.
London: Springer, 2011.

\bibitem{johansen2013control}
Johansen T A, Fossen T I.
Control allocation --- A survey.
\textit{Automatica}, 2013, 49(5): 1087--1103.

\bibitem{markley2014fundamentals}
Markley F L, Crassidis J L.
\textit{Fundamentals of Spacecraft Attitude Determination and Control}.
New York: Springer, 2014.

\bibitem{kuipers1999quaternions}
Kuipers J B.
\textit{Quaternions and Rotation Sequences: A Primer with Applications to Orbits, Aerospace and Virtual Reality}.
Princeton, NJ: Princeton University Press, 1999.

\bibitem{etkin1982dynamics}
Etkin B.
\textit{Dynamics of Atmospheric Flight}.
New York: Wiley, 1982.

\bibitem{stengel2004flight}
Stengel R F.
\textit{Flight Dynamics}.
Princeton, NJ: Princeton University Press, 2004.

\bibitem{beard2012small}
Beard R W, McLain T W.
\textit{Small Unmanned Aircraft: Theory and Practice}.
Princeton, NJ: Princeton University Press, 2012.

\bibitem{mahony2012multirotor}
Mahony R, Kumar V, Corke P.
Multirotor aerial vehicles: Modeling, estimation, and control of quadrotor.
\textit{IEEE Robotics \& Automation Magazine}, 2012, 19(3): 20--32.

\bibitem{ding2018modeling}
Ding C, Wang C, Lu L, Ouyang B.
Modeling and control of fully actuated vector thrust unmanned aerial vehicles.
In: \textit{Proceedings of 2018 International Symposium on Flexible Automation (ISFA)},
Kanazawa, Japan, 2018: Paper ISFA2018-L034.

\bibitem{seguigasco2014novel}
Segui-Gasco P, Al-Rihani Y, Shin H S, Savvaris A.
A novel actuation concept for a multi rotor UAV.
\textit{Journal of Intelligent \& Robotic Systems}, 2014, 74(1): 173--191.

\bibitem{zhu2025experimental}
Zhu H, Du Y, Nie H, Xin Z, Geng X.
Experimental investigation of aerodynamic interaction in non-parallel tandem dual-rotor
systems for tiltrotor UAV.
\textit{Drones}, 2025, 9(5): 374.

\bibitem{oppenheimer2010control}
Oppenheimer M W, Doman D B, Bolender M A.
Control allocation for over-actuated systems.
In: \textit{Proceedings of the 14th Mediterranean Conference on Control and Automation},
2006: 1--6.

\bibitem{kang2009control}
Kang Y, Hedrick J K.
Linear tracking for a fixed-wing UAV using nonlinear model predictive control.
\textit{IEEE Transactions on Control Systems Technology}, 2009, 17(5): 1202--1210.

\bibitem{ducard2008modeling}
Ducard G, Geering H P.
Efficient nonlinear actuator fault detection and isolation system for unmanned aerial vehicles.
\textit{Journal of Guidance, Control, and Dynamics}, 2008, 31(1): 225--237.

\bibitem{kim2003nonlinear}
Kim H J, Shim D H.
A flight control system for aerial robots: algorithms and experiments.
\textit{Control Engineering Practice}, 2003, 11(12): 1389--1400.

% ---------- INDI 相关（第10章）----------
\bibitem{pollack2023robust}
Pollack T, van Kampen E J.
Robust stability and performance analysis of incremental dynamic-inversion-based flight control laws.
\textit{Journal of Guidance, Control, and Dynamics}, 2023, 46(12): 2365--2382.

\bibitem{sieberling2010robust}
Sieberling S, Chu Q P, Mulder J A.
Robust flight control using incremental nonlinear dynamic inversion and angular acceleration prediction.
\textit{Journal of Guidance, Control, and Dynamics}, 2010, 33(6): 1732--1742.

\bibitem{wang2019incremental}
Wang X, van Kampen E J, Chu Q P, et al.
Incremental sliding-mode fault-tolerant flight control.
\textit{Journal of Guidance, Control, and Dynamics}, 2019, 42(2): 244--255.

\bibitem{smeur2016incremental}
Smeur E J J, Chu Q P, de Croon G C H E.
Incremental control and guidance of hybrid aircraft applied to a tailsitter unmanned air vehicle.
\textit{Journal of Guidance, Control, and Dynamics}, 2016, 39(2): 273--287.

\bibitem{grondman2018design}
Grondman F, Looye G, Kuchar R O, et al.
Design and flight testing of incremental nonlinear dynamic inversion-based control laws for a passenger aircraft.
In: \textit{AIAA Guidance, Navigation, and Control Conference}, 2018: 2018-0385.

\bibitem{jiang2026enhanced}
Jiang Y, Li D, Kan Z, et al.
Enhanced incremental nonlinear dynamic inversion with aerodynamic angular rate feedback for autonomous wing rock recovery of a flying-wing UAV.
\textit{Drones}, 2026, 10(6): 433.

\bibitem{schlatter2024longitudinal}
Schlatter M, Ducard G, Rohr D, et al.
Longitudinal control of a tilt-rotor VTOL UAV using incremental nonlinear dynamic inversion.
In: \textit{International Conference on Control, Automation and Diagnosis (ICCAD)}, 2024.

\bibitem{bhandari2024design}
Bhandari A, Luong T, Larson J D.
Design and implementation of an incremental nonlinear dynamic inversion (INDI) based control law for a quad-plane UAV.
In: \textit{IEEE Aerospace Conference}, 2024.

\bibitem{ludena2020flight}
Lude\~{n}a Cervantes T J, Choi S H, Kim B S.
Flight control design using incremental nonlinear dynamic inversion with fixed-lag smoothing estimation.
\textit{International Journal of Aeronautical and Space Sciences}, 2020, 21: 1047--1058.

\bibitem{zhu2026mems}
Zhu M, Liu Q, Zhang H, et al.
MEMS electrochemical angular accelerometer: a paradigm shift for attitude detection and control in rotorcraft UAVs.
\textit{Microsystems \& Nanoengineering}, 2026, 12: 53.

\bibitem{jiang2025adaptive}
Jiang Y, Li D, Kan Z, et al.
Adaptive complementary filter method for aircraft incremental nonlinear dynamic control.
In: \textit{IEEE International Conference on Signal Processing, Communications and Computing (ICSPCC)}, 2025.

\bibitem{levant1998robust}
Levant A.
Robust exact differentiation via sliding mode technique.
\textit{Automatica}, 1998, 34(3): 379--384.

\bibitem{markley2014fundamentals}
Markley F L, Crassidis J L.
\textit{Fundamentals of Spacecraft Attitude Determination and Control}.
Springer, 2014.

\bibitem{wie2008quaternion}
Wie B, Weiss H, Arapostathis A.
Quaternion feedback regulator for spacecraft eigenaxis rotations.
\textit{Journal of Guidance, Control, and Dynamics}, 1989, 12(3): 375--380.

\bibitem{shoemake1985animating}
Shoemake K.
Animating rotation with quaternion curves.
\textit{ACM SIGGRAPH Computer Graphics}, 1985, 19(3): 245--254.

\bibitem{kuipers1999quaternions}
Kuipers J B.
\textit{Quaternions and Rotation Sequences}.
Princeton University Press, 1999.

\end{thebibliography}
